A planetary collision afterglow and transit of the resultant debris cloud

### 2023-10-04 src/tex/ms.tex
[showyourwork] overleaf sync

\usepackage{etoolbox}

@@

% for bibliography
%\usepackage{natbib}
\def\aap{Astron. \& Astrophys.}
\def\aj{Astron. J.}
\def\apj{Astrophys. J.}
\def\apjs{Astrophys. J. Suppl.}
%\let\apjsupp\apjs
\def\apss{Astrophys. Space Sci.}
\def\araa{Ann. Rev. Astron. Astrophys.}
\def\icarus{Icarus}
\def\mnras{Mon. Not. R. Astron. Soc.}
\def\nat{Nature}
\def\pasp{Proc. Astron. Soc. Pac.}
% Package hyperref Warning: Difference (4) between bookmark levels is greater than one, level fixed on input line 1426.
% 
\setcounter{tocdepth}{1}

@@

@@

\abstract{
Planets grow in rotating disks of dust and gas around forming stars, some of which can subsequently collide in giant impacts after the gas component is removed from the disk \cite{Williams11,Wyatt15,Hughes18}.
%
Monitoring programs with the warm Spitzer mission have recorded significant and rapid changes in mid-infrared output for several stars, interpreted as variations in the surface area of warm dusty material ejected by planetary-scale collisions and heated by the central star: e.g., NGC 2354–ID8 \cite{2014Sci...345.1032M,Su19}, HD 166191 \cite{Su22} and V844 Persei \cite{2021ApJ...918...71R}.
%
%However, observational constraints on the aftermath and frequency of such impacts are difficult to obtain.
%
Here we report combined observations of the young ($\sim$~300~Myr), solar-like star \asas{}: an infrared brightening consistent with a blackbody temperature of 1000 K and a luminosity of 4\% of that of the star lasting for about 1000\,days, partially overlapping in time with a complex and deep wavelength-dependent optical eclipse that lasted for about 500 days.
%
The optical eclipse started 2.5\,years after the infrared brightening, implying an orbital period of at least that duration.
%
These observations are consistent with a collision between two exoplanets of several to tens of Earth masses at 2-16\,au from the central star. 
%
Such an impact produces a hot, highly-extended post-impact remnant with sufficient luminosity to explain the infrared observations.
%
Transit of the impact debris, sheared by orbital motion into a long cloud, causes the subsequent complex eclipse of the host star.
}

@@

@@

@@

@@

A key line of evidence for direct detection of a post-impact body is the constant emission temperature.
%
It is argued \cite{Lock18} that rocky post-impact bodies become optically thin at low pressures where radiative loss drives rapid condensation of the rock vapor.
%
The emission temperature is then set by the liquid-vapor phase boundary and is constant until the post-impact body almost fully condenses \cite{Lock18,Caracas2023}.
%
The dew point (onset of condensation) and bubble point (onset of substantial vaporization) of material with bulk silicate Earth composition are similar \cite[$\sim2300$~K, within $\sim 100$~K;][]{Lock18,Fegley2023_BSE_cond} at the low pressures of the photosphere of a post-impact body.
%
However, even small amounts of water (10$^{-3}$ mole fraction) may lower the bubble and dew points for silicates by $\sim$100~K \cite[][]{Fegley2023_BSE_cond,Lock18}. 
%
The emission temperature of bodies produced by collisions of proto-planets composed of rock and ices/volatiles could be buffered at $\sim$1000~K during early evolution.

@@

\clearpage

\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\burl{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}
\providecommand{\doi}[1]{\url{https://doi.org/#1}}
\bibcommenthead

\bibitem{Williams11}
\bibinfo{author}{{Williams}, J.~P.} \& \bibinfo{author}{{Cieza}, L.~A.}
\newblock \bibinfo{title}{{Protoplanetary Disks and Their Evolution}}.
\newblock \emph{\bibinfo{journal}{\araa}} \textbf{\bibinfo{volume}{49}},
  \bibinfo{pages}{67--117} (\bibinfo{year}{2011}).
\newblock \urlprefix\url{http://adsabs.harvard.edu/abs/2011ARA%26A..49...67W}.

\bibitem{Wyatt15}
\bibinfo{author}{{Wyatt}, M.~C.}, \bibinfo{author}{{Pani{\'c}}, O.},
  \bibinfo{author}{{Kennedy}, G.~M.} \& \bibinfo{author}{{Matr{\`a}}, L.}
\newblock \bibinfo{title}{{Five steps in the evolution from protoplanetary to
  debris disk}}.
\newblock \emph{\bibinfo{journal}{\apss}} \textbf{\bibinfo{volume}{357}},
  \bibinfo{pages}{103} (\bibinfo{year}{2015}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2015Ap&SS.357..103W}.

\bibitem{Hughes18}
\bibinfo{author}{{Hughes}, A.~M.}, \bibinfo{author}{{Duch{\^e}ne}, G.} \&
  \bibinfo{author}{{Matthews}, B.~C.}
\newblock \bibinfo{title}{{Debris Disks: Structure, Composition, and
  Variability}}.
\newblock \emph{\bibinfo{journal}{\araa}} \textbf{\bibinfo{volume}{56}},
  \bibinfo{pages}{541--591} (\bibinfo{year}{2018}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2018ARA&A..56..541H}.

\bibitem{2014Sci...345.1032M}
\bibinfo{author}{{Meng}, H. Y.~A.} \emph{et~al.}
\newblock \bibinfo{title}{{Large impacts around a solar-analog star in the era
  of terrestrial planet formation}}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{345}},
  \bibinfo{pages}{1032--1035} (\bibinfo{year}{2014}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2014Sci...345.1032M}.

\bibitem{Su19}
\bibinfo{author}{{Su}, K. Y.~L.} \emph{et~al.}
\newblock \bibinfo{title}{{Extreme Debris Disk Variability: Exploring the
  Diverse Outcomes of Large Asteroid Impacts During the Era of Terrestrial
  Planet Formation}}.
\newblock \emph{\bibinfo{journal}{\aj}} \textbf{\bibinfo{volume}{157}},
  \bibinfo{pages}{202} (\bibinfo{year}{2019}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2019AJ....157..202S}.

\bibitem{Su22}
\bibinfo{author}{{Su}, K. Y.~L.}, \bibinfo{author}{{Kennedy}, G.~M.},
  \bibinfo{author}{{Schlawin}, E.}, \bibinfo{author}{{Jackson}, A.~P.} \&
  \bibinfo{author}{{Rieke}, G.~H.}
\newblock \bibinfo{title}{{A Star-sized Impact-produced Dust Clump in the
  Terrestrial Zone of the HD 166191 System}}.
\newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{927}},
  \bibinfo{pages}{135} (\bibinfo{year}{2022}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2022ApJ...927..135S}.

\bibitem{2021ApJ...918...71R}
\bibinfo{author}{{Rieke}, G.~H.}, \bibinfo{author}{{Su}, K.~Y.~L.},
  \bibinfo{author}{{Melis}, C.} \& \bibinfo{author}{{G{\'a}sp{\'a}r}, A.}
\newblock \bibinfo{title}{{Extreme Variability of the V488 Persei Debris
  Disk}}.
\newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{918}},
  \bibinfo{pages}{71} (\bibinfo{year}{2021}).

\bibitem{RizzoSmith21}
\bibinfo{author}{{Rizzo Smith}, M.} \emph{et~al.}
\newblock \bibinfo{title}{{ASASSN-21qj: A Rapidly Fading, Sun-Like Star}}.
\newblock \emph{\bibinfo{journal}{The Astronomer's Telegram}}
  \textbf{\bibinfo{volume}{14879}}, \bibinfo{pages}{1} (\bibinfo{year}{2021}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2021ATel14879....1R}.

\bibitem{RizzoSmith22}
\bibinfo{author}{{Rizzo Smith}, M.} \emph{et~al.}
\newblock \bibinfo{title}{{An Update on ASASSN-21qj: A Rapidly Fading, Sun-Like
  Star; Back With a Vengeance}}.
\newblock \emph{\bibinfo{journal}{The Astronomer's Telegram}}
  \textbf{\bibinfo{volume}{15531}}, \bibinfo{pages}{1} (\bibinfo{year}{2022}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2022ATel15531....1R}.

\bibitem{shappee_man_2014}
\bibinfo{author}{Shappee, B.~J.} \emph{et~al.}
\newblock \bibinfo{title}{The {Man} behind the {Curtain}: {X}-{Rays} {Drive}
  the {UV} through {NIR} {Variability} in the 2013 {Active} {Galactic}
  {Nucleus} {Outburst} in {NGC} 2617}.
\newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{788}},
  \bibinfo{pages}{48} (\bibinfo{year}{2014}).
\newblock \urlprefix\url{http://adsabs.harvard.edu/abs/2014ApJ...788...48S}.

\bibitem{kochanek_all-sky_2017}
\bibinfo{author}{Kochanek, C.~S.} \emph{et~al.}
\newblock \bibinfo{title}{The {All}-{Sky} {Automated} {Survey} for {Supernovae}
  ({ASAS}-{SN}) {Light} {Curve} {Server} v1.0}.
\newblock \emph{\bibinfo{journal}{Publications of the Astronomical Society of
  the Pacific}} \textbf{\bibinfo{volume}{129}}, \bibinfo{pages}{104502}
  (\bibinfo{year}{2017}).
\newblock \urlprefix\url{http://adsabs.harvard.edu/abs/2017PASP..129j4502K}.

\bibitem{Lock2017}
\bibinfo{author}{Lock, S.~J.} \& \bibinfo{author}{Stewart, S.~T.}
\newblock \bibinfo{title}{The structure of terrestrial bodies: {Impact}
  heating, corotation limits, and synestias}.
\newblock \emph{\bibinfo{journal}{Journal of Geophysical Research: Planets}}
  \textbf{\bibinfo{volume}{122}}, \bibinfo{pages}{950--982}
  (\bibinfo{year}{2017}).
\newblock \urlprefix\url{http://doi.wiley.com/10.1002/2016JE005239}.

\bibitem{2009ApJ...704..770M}
\bibinfo{author}{{Miller-Ricci}, E.}, \bibinfo{author}{{Meyer}, M.~R.},
  \bibinfo{author}{{Seager}, S.} \& \bibinfo{author}{{Elkins-Tanton}, L.}
\newblock \bibinfo{title}{{On the Emergent Spectra of Hot Protoplanet Collision
  Afterglows}}.
\newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{704}},
  \bibinfo{pages}{770--780} (\bibinfo{year}{2009}).

\bibitem{Schlichting2018a}
\bibinfo{author}{Schlichting, H.~E.}
\newblock \bibinfo{title}{ in \textit{Formation of super-{Earths}}} (eds
  \bibinfo{editor}{Hans, D.} \& \bibinfo{editor}{Belmonte, J.~A.})
  \emph{\bibinfo{booktitle}{Handbook of {Exoplanets}}}
  (\bibinfo{publisher}{Springer}, \bibinfo{year}{2018}).
\newblock \urlprefix\url{http://arxiv.org/abs/1802.03090}.
\newblock \bibinfo{note}{ArXiv: 1802.03090}.

\bibitem{DAngelo2018}
\bibinfo{author}{D’Angelo, G.} \& \bibinfo{author}{Lissauer, J.~J.}
\newblock \bibinfo{title}{ in \textit{Formation of {Giant} {Planets}}} (eds
  \bibinfo{editor}{Deeg, H.~J.} \& \bibinfo{editor}{Belmonte, J.~A.})
  \emph{\bibinfo{booktitle}{Handbook of {Exoplanets}}} \bibinfo{pages}{1--25}
  (\bibinfo{publisher}{Springer International Publishing},
  \bibinfo{address}{Cham}, \bibinfo{year}{2018}).
\newblock \urlprefix\url{https://doi.org/10.1007/978-3-319-30648-3_140-2}.

\bibitem{Kaib2016}
\bibinfo{author}{Kaib, N.~A.} \& \bibinfo{author}{Chambers, J.~E.}
\newblock \bibinfo{title}{The fragility of the terrestrial planets during a
  giant-planet instability}.
\newblock \emph{\bibinfo{journal}{\mnras}} \textbf{\bibinfo{volume}{455}},
  \bibinfo{pages}{3561--3569} (\bibinfo{year}{2016}).
\newblock \urlprefix\url{https://doi.org/10.1093/mnras/stv2554}.

\bibitem{Nakajima2015}
\bibinfo{author}{Nakajima, M.} \& \bibinfo{author}{Stevenson, D.~J.}
\newblock \bibinfo{title}{Melting and mixing states of the {Earth}'s mantle
  after the {Moon}-forming impact}.
\newblock \emph{\bibinfo{journal}{Earth and Planetary Science Letters}}
  \textbf{\bibinfo{volume}{427}}, \bibinfo{pages}{286--295}
  (\bibinfo{year}{2015}).
\newblock
  \urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0012821X15003805}.

\bibitem{Carter2020}
\bibinfo{author}{Carter, P.~J.}, \bibinfo{author}{Lock, S.~J.} \&
  \bibinfo{author}{Stewart, S.~T.}
\newblock \bibinfo{title}{The {Energy} {Budgets} of {Giant} {Impacts}}.
\newblock \emph{\bibinfo{journal}{Journal of Geophysical Research: Planets}}
  \textbf{\bibinfo{volume}{125}} (\bibinfo{year}{2020}).
\newblock \bibinfo{note}{ArXiv: 1912.04936}.

\bibitem{Canup2001}
\bibinfo{author}{Canup, R.~M.} \& \bibinfo{author}{Asphaug, E.}
\newblock \bibinfo{title}{Origin of the {Moon} in a giant impact near the end
  of the {Earth}'s formation}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{412}},
  \bibinfo{pages}{708--12} (\bibinfo{year}{2001}).
\newblock \urlprefix\url{http://dx.doi.org/10.1038/35089010}.

\bibitem{Lock18}
\bibinfo{author}{{Lock}, S.~J.} \emph{et~al.}
\newblock \bibinfo{title}{{The Origin of the Moon Within a Terrestrial
  Synestia}}.
\newblock \emph{\bibinfo{journal}{Journal of Geophysical Research (Planets)}}
  \textbf{\bibinfo{volume}{123}}, \bibinfo{pages}{910--951}
  (\bibinfo{year}{2018}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2018JGRE..123..910L}.

\bibitem{Benz2008_Mercury_book}
\bibinfo{author}{Benz, W.}, \bibinfo{author}{Anic, A.},
  \bibinfo{author}{Horner, J.} \& \bibinfo{author}{Whitby, J.~A.}
\newblock \bibinfo{title}{ in \textit{The {Origin} of {Mercury}}} (eds
  \bibinfo{editor}{Balogh, A.}, \bibinfo{editor}{Ksanfomality, L.} \&
  \bibinfo{editor}{von Steiger, R.}) \emph{\bibinfo{booktitle}{Mercury}} Space
  {Sciences} {Series} of {ISSI}, \bibinfo{pages}{7--20}
  (\bibinfo{publisher}{Springer}, \bibinfo{address}{New York, NY},
  \bibinfo{year}{2008}).
\newblock \urlprefix\url{https://doi.org/10.1007/978-0-387-77539-5_2}.

\bibitem{Leinhardt2015}
\bibinfo{author}{Leinhardt, Z.~M.}, \bibinfo{author}{Dobinson, J.},
  \bibinfo{author}{Carter, P.~J.} \& \bibinfo{author}{Lines, S.}
\newblock \bibinfo{title}{Numerically predicted indirect signatures of
  terrestrial planet formation}.
\newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{806}},
  \bibinfo{pages}{23} (\bibinfo{year}{2015}).
\newblock \urlprefix\url{https://doi.org/10.1088/0004-637X/806/1/23}.

\bibitem{Carter2020a}
\bibinfo{author}{Carter, P.~J.} \& \bibinfo{author}{Stewart, S.~T.}
\newblock \bibinfo{title}{Colliding in the {Shadows} of {Giants}:
  {Planetesimal} {Collisions} during the {Growth} and {Migration} of {Gas}
  {Giants}}.
\newblock \emph{\bibinfo{journal}{The Planetary Science Journal}}
  \textbf{\bibinfo{volume}{1}}, \bibinfo{pages}{45} (\bibinfo{year}{2020}).
\newblock \urlprefix\url{https://doi.org/10.3847/PSJ/abaecc}.
\newblock \bibinfo{note}{ArXiv: 2008.05549 Publisher: IOP Publishing}.

\bibitem{Stewart2008}
\bibinfo{author}{Stewart, S.~T.}, \bibinfo{author}{Seifter, A.} \&
  \bibinfo{author}{Obst, A.~W.}
\newblock \bibinfo{title}{Shocked {H2O} ice: {Thermal} emission measurements
  and the criteria for phase changes during impact events}.
\newblock \emph{\bibinfo{journal}{Geophysical Research Letters}}
  \textbf{\bibinfo{volume}{35}}, \bibinfo{pages}{L23203}
  (\bibinfo{year}{2008}).
\newblock \urlprefix\url{http://doi.wiley.com/10.1029/2008GL035947}.
\newblock \bibinfo{note}{ISBN: 0094-8276}.

\bibitem{Davies2020}
\bibinfo{author}{Davies, E.~J.} \emph{et~al.}
\newblock \bibinfo{title}{Silicate {Melting} and {Vaporization} {During}
  {Rocky} {Planet} {Formation}}.
\newblock \emph{\bibinfo{journal}{Journal of Geophysical Research: Planets}}
  \textbf{\bibinfo{volume}{125}} (\bibinfo{year}{2020}).
\newblock
  \urlprefix\url{https://onlinelibrary.wiley.com/doi/abs/10.1029/2019JE006227}.
\newblock \bibinfo{note}{ArXiv: 2002.00998 Publisher: John Wiley \& Sons, Ltd}.

\bibitem{Johnson2015}
\bibinfo{author}{Johnson, B.~C.}, \bibinfo{author}{Minton, D.~A.},
  \bibinfo{author}{Melosh, H.~J.} \& \bibinfo{author}{Zuber, M.~T.}
\newblock \bibinfo{title}{Impact jetting as the origin of chondrules}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{517}},
  \bibinfo{pages}{339--341} (\bibinfo{year}{2015}).
\newblock \urlprefix\url{http://dx.doi.org/10.1038/nature14105}.
\newblock \bibinfo{note}{Publisher: Nature Publishing Group, a division of
  Macmillan Publishers Limited. All Rights Reserved.}

\bibitem{Caracas2023}
\bibinfo{author}{Caracas, R.} \& \bibinfo{author}{Stewart, S.~T.}
\newblock \bibinfo{title}{No magma ocean surface after giant impacts between
  rocky planets}.
\newblock \emph{\bibinfo{journal}{Earth and Planetary Science Letters}}
  \textbf{\bibinfo{volume}{608}}, \bibinfo{pages}{118014}
  (\bibinfo{year}{2023}).
\newblock
  \urlprefix\url{https://www.sciencedirect.com/science/article/pii/S0012821X23000274}.

\bibitem{Fegley2023_BSE_cond}
\bibinfo{author}{Fegley, B.}, \bibinfo{author}{Lodders, K.} \&
  \bibinfo{author}{Jacobson, N.~S.}
\newblock \bibinfo{title}{Chemical equilibrium calculations for bulk silicate
  earth material at high temperatures}.
\newblock \emph{\bibinfo{journal}{Geochemistry}} \bibinfo{pages}{125961}
  (\bibinfo{year}{2023}).
\newblock
  \urlprefix\url{https://www.sciencedirect.com/science/article/pii/S0009281923000120}.

\bibitem{Lock2018moon}
\bibinfo{author}{Lock, S.~J.} \emph{et~al.}
\newblock \bibinfo{title}{The origin of the {Moon} within a terrestrial
  synestia}.
\newblock \emph{\bibinfo{journal}{Journal of Geophysical Research: Planets}}
  \textbf{\bibinfo{volume}{123}}, \bibinfo{pages}{910--951}
  (\bibinfo{year}{2018}).
\newblock \urlprefix\url{http://doi.wiley.com/10.1002/2017JE005333}.
\newblock \bibinfo{note}{ArXiv: 1802.10223v1}.

\bibitem{Lock2020}
\bibinfo{author}{Lock, S.~J.}, \bibinfo{author}{Stewart, S.~T.} \&
  \bibinfo{author}{Ćuk, M.}
\newblock \bibinfo{title}{The energy budget and figure of {Earth} during
  recovery from the {Moon}-forming giant impact}.
\newblock \emph{\bibinfo{journal}{Earth and Planetary Science Letters}}
  \textbf{\bibinfo{volume}{530}}, \bibinfo{pages}{115885}
  (\bibinfo{year}{2020}).
\newblock \urlprefix\url{https://doi.org/10.1016/j.epsl.2019.115885}.
\newblock \bibinfo{note}{ArXiv: 1910.00619 Publisher: Elsevier}.

%%%%%%%%%%%
%%% 30
%%%%%%%%%%%%

\end{thebibliography}

\clearpage

>>>>

% separate reference sections for the article and the Method
% https://www.overleaf.com/learn/latex/Questions/Creating_multiple_bibliographies_in_the_same_document#The_multibib_package
% \usepackage[sectionbib]{bibunits}
% \defaultbibliographystyle{sn-nature} 
% \defaultbibliography{sn-bibliography}

@@

% for bibliography
%\usepackage{natbib}
\def\aap{Astron. \& Astrophys.}
\def\aj{Astron. J.}
\def\apj{Astrophys. J.}
\def\apjs{Astrophys. J. Suppl.}
%\let\apjsupp\apjs
\def\apss{Astrophys. Space Sci.}
\def\araa{Ann. Rev. Astron. Astrophys.}
\def\icarus{Icarus}
\def\mnras{Mon. Not. R. Astron. Soc.}
\def\nat{Nature}
\def\pasp{Proc. Astron. Soc. Pac.}
% Package hyperref Warning: Difference (4) between bookmark levels is greater than one, level fixed on input line 1426.
%

% \def\apjl{ApJL}
% \def\aj{AJ}
% \def\apj{ApJ}
% \def\pasp{PASP}
% \def\spie{SPIE}
% \def\apjs{ApJS}
% \def\araa{ARAA}
% \def\mnras{MNRAS}
% \def\aap{A\&A}
% \def\nat{Nature}
% \def\icarus{Icarus}

\setcounter{tocdepth}{1}

@@

%%=============================================================%%
%% Prefix	-> \pfx{Dr}
%% GivenName	-> \fnm{Joergen W.}
%% Particle	-> \spfx{van der} -> surname prefix
%% FamilyName	-> \sur{Ploeg}
%% Suffix	-> \sfx{IV}
%% NatureName	-> \tanm{Poet Laureate} -> Title after name
%% Degrees	-> \dgr{MSc, PhD}
%% \author*[1,2]{\pfx{Dr} \fnm{Joergen W.} \spfx{van der} \sur{Ploeg} \sfx{IV} \tanm{Poet Laureate} 
%%                 \dgr{MSc, PhD}}\email{iauthor@gmail.com}
%%=============================================================%%

@@

%%==================================%%
%% sample for unstructured abstract %%
%%==================================%%

\abstract{
Planets grow in rotating disks of dust and gas around forming stars, some of which can subsequently collide in giant impacts after the gas component is removed from the disk \cite{Williams11,Wyatt15,Hughes18}.
%
%The remaining solid material forms so-called debris disks which contain planetesimals that, through collisional cascades, generate large amounts of dust that are heated by the star to black body temperatures of 70 to 300\,K \cite{Chen06,Hillenbrand08}.
%
%These are detected as excess infrared emission \cite{Wyatt08,Rieke05,Su06} that decays smoothly with time as the dust is depleted  \cite{2003ApJ...598..626D,Kenyon04,Wyatt08}.
%
%Collisions between planets are a key process in planet formation \citep{Schlichting2018a,DAngelo2018}. 
%
Monitoring programs with the warm Spitzer mission have recorded significant and rapid changes in mid-infrared output for several stars, interpreted as variations in the surface area of warm dusty material ejected by planetary-scale collisions and heated by the central star: e.g., NGC 2354–ID8 \cite{2014Sci...345.1032M,Su19}, HD 166191 \cite{Su22} and V844 Persei \cite{2021ApJ...918...71R}.
%
%However, observational constraints on the aftermath and frequency of such impacts are difficult to obtain.
%
Here we report combined observations of the young ($\sim$~300~Myr), solar-like star \asas{}: an infrared brightening consistent with a blackbody temperature of 1000 K and a luminosity of 4\% of that of the star lasting for about 1000\,days, partially overlapping in time with a complex and deep wavelength-dependent optical eclipse that lasted for about 500 days.
%
The optical eclipse started 2.5\,years after the infrared brightening, implying an orbital period of at least that duration.
%
These observations are consistent with a collision between two exoplanets of several to tens of Earth masses at 2-16\,au from the central star. 
%
Such an impact produces a hot, highly-extended post-impact remnant with sufficient luminosity to explain the infrared observations.
%
Transit of the impact debris, sheared by orbital motion into a long cloud, causes the subsequent complex eclipse of the host star.
%
% Direct observation of a post-impact remnant will revolutionize our understanding of giant impacts, and continued observations will provide new insight into the processes of planet formation.
}

% % █ █▄░█ ▀█▀ █▀█ █▀█ █▀▄ █░█ █▀▀ ▀█▀ █ █▀█ █▄░█
% % █ █░▀█ ░█░ █▀▄ █▄█ █▄▀ █▄█ █▄▄ ░█░ █ █▄█ █░▀█

% Planets grow in rotating disks of dust and gas around forming stars. 
% %
% Towards the end of the planet-forming epoch the majority of the circumstellar gas is removed through accretion on to the star, photoevaporation, and stellar winds \cite{Williams11,Wyatt15,Hughes18}. The solid material that is left behind, ranging from dust to planetary embryos, forms so-called debris disks. These disks are analogues of the Solar system's Asteroid and Edgeworth-Kuiper belts.
% %
% Freed of the damping effects of the gas, collisional cascades break down planetesimals that orbit the star into smaller and smaller debris, until the smallest grains are cleared out of the system by the radiation pressure from the star \cite{Wyatt08}.
% %
% This dust is heated by the star, producing infrared emission with spectral energy distributions described with black body temperatures of 70 to 300\,K \cite{Chen06,Hillenbrand08} and constant fractional luminosities $f = L_{dust}/L_{star}<10^{-3}$ \cite{Wyatt08}.
% %
% The brightness of these disks falls with increasing age, consistent with depletion of material from the birth belts as predicted by theory \cite{2003ApJ...598..626D,Kenyon04,Wyatt08} and agreeing with observational studies \cite{Rieke05,Su06}.
% %
% However, superimposed on this smooth decay are sudden outbursts of flux from large  dust clouds produced by energetic collisions between the largest planetesimals and/or planetary embryos  \cite{2007ApJ...658..569W,2012Natur.487...74M,Meng12,Schneider13}.
% %
% Monitoring programs with the warm Spitzer mission have recorded significant and rapid changes in mid-infrared output consistent with planetary collisions around several stars, e.g., NGC 2354–ID8 \cite{2014Sci...345.1032M,Su19}, HD 166191 \cite{Su22}. 
% %
% These systems are referred to as Extreme Debris Disks \cite[EDDs;][]{Balog09} due to their warmer dust temperatures and significantly higher infrared luminosity compared to a typical debris disk ($f \gtrsim 10^{-2}$).

@@

\begin{figure}
\begin{centering}
\includegraphics[width=\textwidth]{all_phot_nature_delta_flux.pdf}
\caption{Optical and infrared photometry of ASASSN-21qj.
%
Panel {\bf a} is normalised optical photometry from ASAS-SN in $V$-band and $g'$ band.
%
Panel {\bf b} shows the fractional flux increase in brightness of ASASSN-21qj in both the $W1$ and $W2$ bands, where a value of 1.0 represents the stellar contribution alone.
%
Panel {\bf c} shows the calculated $NEOWISE$ color temperature estimated from the photometry of the two bands.
%
The color temperature is plotted as zero when there is no IR excess, and is consistent with a temperature of 1000\,K while the excess is present.
%
Error bars are shown at $1\sigma$ confidence.
}
\label{fig:wisephot}
%\script{plot_all_photometry.py}
\end{centering}
\end{figure}

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=1.0\textwidth]{master_lightcurve_nature_simple.pdf}
      \caption{The light curve of ASASSN-21qj from several different photometric surveys and the derived transverse velocities.
      %
      Panel {\bf a} shows that the eclipse depth is deeper for shorter wavelengths, indicating that the transiting material is dominated by sub-micron sized grains.
      %
      Panel {\bf b} shows the  transverse velocities derived from the light curve gradients.
      %
      These are lower limits to the true velocity, and thus imply that the transiting material is closer to the star than 16\,au.
      %
      Error bars are shown at $1\sigma$ confidence.
      }
        \label{fig:eclipse_overview}
 %       \script{plot_master_lightcurve.py}
\end{centering}
\end{figure*}

@@

% % 291 words
% \begin{figure}
% \begin{centering}
% \includegraphics[width=\columnwidth]{Hill_Bondi_radii.pdf}
% \caption{A post-impact body of a few to tens of Earth masses could be large enough to explain the observed increase in thermal emission from ASASSN-21qj.
% %
% Shown are the Hill radii for bodies at different semi-major axis (solid colored lines) and the Bondi radii (dotted lines) assuming different compositions for the relevant vapor.
% %
% The horizontal black dashed line shows the radii required to explain the observed flux at the inferred emission temperature of 1000~K. 
% }
% \label{fig:Hill_Bondi_R}
% \end{centering}
% \end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=\columnwidth]{Size_cooling_combined_figure.pdf}
\caption{The size and temporal evolution of a post-impact body.
%
A post-impact body of a few to tens of Earth masses could be large enough to explain the observed increase in thermal emission from ASASSN-21qj and the subsequent infrared fluxes.
%
Panel {\bf a} shows the Hill radii for bodies at different semi-major axis (solid colored lines) and the Bondi radii (dotted lines) assuming different compositions for the vapor of the post-impact body.
%
The horizontal black dashed line shows the radii required to explain the observed flux at the inferred emission temperature of 1000~K. 
%
The change in excess flux due to a post-impact body with time for a simple model of cooling of a post-impact body for different power-law surface density profiles is in panel {\bf b}, eqn~\ref{eqn:sigma} and for different mass bodies in panel {\bf c}.
%
Each example had an initial radius of 7\,$R_\odot$, a radiative temperature of 1000~K, and a corresponding initial flux of 0.04\,$L_\star$, as estimated for the observed infrared emittor.
%
The solid lines are profiles that can have non-zero initial density at the initial emitting radius, and the dashed lines are for ones that are forced to have zero density at the initial emitting radius.
%
When not stated, the mass of the post-impact body was 50~$M_{\rm Earth}$, the power law exponent is $-2$, and the size of the central region was 10~$R_{\rm Earth}$.
}
\label{fig:Hill_Bondi_R}
\end{centering}
\end{figure}

@@

A key line of evidence for direct detection of a post-impact body is the constant emission temperature.
%
It is argued \cite{Lock18} that rocky post-impact bodies become optically thin at low pressures where radiative loss drives rapid condensation of the rock vapor.
%
The emission temperature is then set by the liquid-vapor phase boundary and is constant until the post-impact body almost fully condenses \cite{Lock18,Caracas2023}.
%
The dew point (onset of condensation) and bubble point (onset of substantial vaporization) of material with bulk silicate Earth composition are similar \cite[$\sim2300$~K, within $\sim 100$~K;][]{Lock18,Fegley2023_BSE_cond} at the low pressures of the photosphere of a post-impact body.
%
%This high temperature is inconsistent with our observations, but the control of emission temperature by the thermodynamics of a material would apply in bodies with different compositions, producing varying radiative temperatures. Specifically, given that we infer the post-impact body to be beyond a few au, water is a likely constituent.
%
%At the low pressures of the photosphere of a post-impact body, water has a vaporization temperature of $\sim250$~K \cite[][]{Wagner2002}, much lower than silicates, but too low to explain the observed $\sim$1000~K emission. 
%
%However, a mixture of water and rock (and potentially other constituents) would have intermediate bubble and dew point temperatures. 
However, even small amounts of water (10$^{-3}$ mole fraction) may lower the bubble and dew points for silicates by $\sim$100~K \cite[][]{Fegley2023_BSE_cond,Lock18}. 
%
The emission temperature of bodies produced by collisions of proto-planets composed of rock and ices/volatiles could be buffered at $\sim$1000~K during early evolution.

@@

% 195 words

% █▀▀ █▀█ █▄░█ █▀▀ █░░ █░█ █▀ █ █▀█ █▄░█ █▀
% █▄▄ █▄█ █░▀█ █▄▄ █▄▄ █▄█ ▄█ █ █▄█ █░▀█ ▄█

% We expect the next decade will result in the detection of several dozen transiting systems similar to \asas, through large scale surveys and triggers provided by ASAS-SN.
% %
% Such observations present an opportunity to study the substructure of debris from planetary collisions, and potentially direct observation of more post-impact bodies.

% Direct observation of a post-impact body would be the first of its kind and offer a valuable insight into key process of planetary system formation  and evolution processes, highly complementary to observations of debris disks and disintegrating planetary material \cite{Gaensike2019,Turner2020,Putirka2021,Blouin2020}.
%
% Furthermore, an impact with enough energy to produce the observed flux could result in the formation of a synestia - a hypothesised class of structures that are likely a common outcome of giant impacts \citep{Lock17}.
%
% Detection of a synestia would transfer a theoretical prediction into a newly-accessible class of planetary object.
%
%It is therefore necessary to obtain rigorous confirmation of any such interpretation of observations.
%
%Possible future observations include IR high contrast imaging to ascertain if the 4-5 microns excess remains a point source, as expected for a post-impact body, or is now extended.
%
%Orbital motion over the next few years will place the post-impact body at about 50 milliarcseconds from the star, marginally resolvable with IR imagers on 8m class telescopes, such as the ERIS camera on the VLT.
%
%In addition, long wavelength spectroscopy could reveal emission or absorption features of silicates or volatiles in the post-impact body.
%
% \asas is a prime target for longer wavelength observations, such as MIRI with the JWST.
%

% , and the substructure of circumplanetary disks that are home to exomoon formation, providing an additional detection and characterisation channel.
%

%\putbib
% 115 words
\clearpage
